Monte Carlo calculation to characterize neutron and gamma fields for ANITA neutron facility at TSL

### 2015-04-17 Paper2015.tex
working processing
working process

\begin{figure}[t]
    \vspace{2in}
    \includegraphics[width=3in]{SUP10ColSpatialDistribution10MeVRADECS.png}
% \todo{Show density of neutrons above \SI{10}{\MeV} at SUP}
    \caption{Neutron fluence rate above \SI{10}{\MeV} at the Standard User Position.}
    \label{fig:SUPDensity}
\end{figure}

\begin{figure}[t]
    \vspace{2in}
    \includegraphics[width=3in]{SUP10beamproFoldingRADECS.png}
% \todo{Show SUP profile, compared to measurements}
    \caption{Neutron profile at the Standard User Position}
    \label{fig:SUPProfile}
\end{figure}

@@

\begin{figure}[t]
    \vspace{2in}
%	\subfloat[Integral fluence rate]{\todo{Integral spectra on log-log axes}\hspace{\columnwidth}}\\
	\subfloat[Integral fluence rate]{\includegraphics[width=3in]{SUPcomparedIFluxRADECS.eps}\hspace{\columnwidth}}\\
    \vspace{2in}
%	\subfloat[Equilethargic spectrum, normalised to fluence above \SI{10}{\MeV}]{\todo{Normalised spectra on lethargy axes}\hspace{\columnwidth}}
	\subfloat[Equilethargic spectrum, normalised to fluence above \SI{10}{\MeV}]{\includegraphics[width=3in]{SUPNormalisedRADECS.eps}\hspace{\columnwidth}}
	\caption{Neuton spectrum at the SUP, showing comparison between the standard facility parameterisation~\cite{Prokofiev2009} and results from a naked Geant4 model~\cite{Platt13} and this work.}
	\label{fig:SUPSpectraComparison}
\end{figure}

@@

\begin{figure}[t]
    \vspace{2in}
    \includegraphics[width=3in]{CUP10ColSpatialDistribution10MeV.png}
% \todo{Show density of neutrons above \SI{10}{\MeV} at CUP}
    \caption{Neutron fluence rate above \SI{10}{\MeV} at the Close User Position.}
    \label{fig:CUPDensity}
\end{figure}

\begin{figure}[t]
    \vspace{2in}
    \includegraphics[width=3in]{CUPTOF10beamproRADECS.png}
% \todo{Show CUP profile, compared to measurements}
    \caption{Neutron profile at the Close User Position}
    \label{fig:CUPProfile}
\end{figure}

@@

\begin{figure}[t]
    \vspace{2in}
	\subfloat[Integral fluence rate]{\todo{Integral spectra on log-log axes: CUP}\hspace{\columnwidth}}\\
    \vspace{2in}
	\subfloat[Equilethargic spectrum, normalised to fluence above \SI{10}{\MeV}]{\todo{Normalised spectra on lethargy axes: CUP}\hspace{\columnwidth}}
	\caption{Neuton spectrum at the Close User Position, showing comparison between the standard facility parameterisation~\cite{Prokofiev2009} and results from this work.}
	\label{fig:CUPSpectraComparison}
\end{figure}

@@

\begin{figure}
    \centering
    \vspace{2in}
    \subfloat[SUP]{
%	SUP10ColSpatialDistributionAllG
        \todo{Add gamma spatial distribution at SUP, \SI{10.2}{\cm} collimator}\hspace{\columnwidth}
        \label{fig:GammaSpatialDistributionSUP}
    }\\
    \subfloat[CUP]{
%    CUP10ColSpatialDistributionAllG
        \todo{Add gamma spatial distribution at CUP, \SI{10.2}{\cm} collimator}\hspace{\columnwidth}
        \label{fig:GammaSpatialDistributionCUP}
    }
    \caption{Gamma spatial distribution}
    \todo{It would be better if gamma spatial distribution were expressed as dose, rather than number of photons. Not in time for the abstract submission, however!}
    \label{fig:GammaSpatialDistribution}
\end{figure}

@@

\begin{figure}
    \centering
    \vspace{2in}
    \subfloat[SUP]{
        \todo{Add gamma dose versus energy at SUP, \SI{10.2}{\cm} collimator}\hspace{\columnwidth}
        \label{fig:GammaDoseEnergySUP}
    }\\
    \subfloat[CUP]{
        \todo{Add gamma dose versus energy at CUP, \SI{10.2}{\cm} collimator}\hspace{\columnwidth}
        \label{fig:GammaDoseEnergyCUP}
    }
    \caption{Gamma dose spectra}
    \label{fig:GammaDoseEnergy}
\end{figure}

>>>>

\begin{figure}[t]
%    \vspace{2in}
    \includegraphics[width=3in]{SUP10ColSpatialDistribution10MeVRADECS.png}
% \todo{Show density of neutrons above \SI{10}{\MeV} at SUP}
    \caption{Neutron fluence rate above \SI{10}{\MeV} at the Standard User Position.}
    \label{fig:SUPDensity}
\end{figure}

\begin{figure}[t]
%    \vspace{2in}
    \includegraphics[width=3in]{SUP10beamproFoldingRADECS.png}
% \todo{Show SUP profile, compared to measurements}
    \caption{Neutron profile at the Standard User Position}
    \label{fig:SUPProfile}
\end{figure}

@@

\begin{figure}[t]
%    \vspace{2in}
%	\subfloat[Integral fluence rate]{\todo{Integral spectra on log-log axes}\hspace{\columnwidth}}\\
	\subfloat[Integral fluence rate]{\includegraphics[width=3in]{SUPcomparedIFluxRADECS.eps}\hspace{\columnwidth}}\\
%    \vspace{2in}
%	\subfloat[Equilethargic spectrum, normalised to fluence above \SI{10}{\MeV}]{\todo{Normalised spectra on lethargy axes}\hspace{\columnwidth}}
	\subfloat[Equilethargic spectrum, normalised to fluence above \SI{10}{\MeV}]{\includegraphics[width=3in]{SUPNormalisedRADECS.eps}\hspace{\columnwidth}}
	\caption{Neuton spectrum at the SUP, showing comparison between the standard facility parameterisation~\cite{Prokofiev2009} and results from a naked Geant4 model~\cite{Platt13} and this work.}
	\label{fig:SUPSpectraComparison}
\end{figure}

@@

\begin{figure}[t]
%    \vspace{2in}
    \includegraphics[width=3in]{CUP10ColSpatialDistribution10MeV.png}
% \todo{Show density of neutrons above \SI{10}{\MeV} at CUP}
    \caption{Neutron fluence rate above \SI{10}{\MeV} at the Close User Position.}
    \label{fig:CUPDensity}
\end{figure}

\begin{figure}[t]
%    \vspace{2in}
    \includegraphics[width=3in]{CUPTOF10beamproRADECS.png}
% \todo{Show CUP profile, compared to measurements}
    \caption{Neutron profile at the Close User Position}
    \label{fig:CUPProfile}
\end{figure}

@@

\begin{figure}[t]
%    \vspace{2in}
	\subfloat[Integral fluence rate]{\includegraphics[width=2.5in]{CUPcomparedProkofiev2014linearspaceIFlux.eps}\hspace{\columnwidth}}\\
%    \vspace{2in}
	\subfloat[Equilethargic spectrum, normalised to fluence above \SI{10}{\MeV}]{\includegraphics[width=3in]{CUPcomparedLetFluxRADECS.png}\hspace{\columnwidth}}
	\caption{Neuton spectrum at the Close User Position, showing comparison between the standard facility parameterisation~\cite{Prokofiev2009} and results from this work.}
	\label{fig:CUPSpectraComparison}
\end{figure}

@@

\begin{figure}
    \centering
    \vspace{2in}
    \subfloat[SUP]{\includegraphics[width=3in]{SUP10ColSpatialDistributionAllG.png}
%     \todo{Add gamma spatial distribution at SUP, \SI{10.2}{\cm} collimator}\hspace{\columnwidth}
        \label{fig:GammaSpatialDistributionSUP}
    }\\
    \subfloat[CUP]{\includegraphics[width=3in]{CUP10ColSpatialDistributionAllG.png}
%     \todo{Add gamma spatial distribution at CUP, \SI{10.2}{\cm} collimator}\hspace{\columnwidth}
        \label{fig:GammaSpatialDistributionCUP}
    }
    \caption{Gamma spatial distribution}
    \todo{It would be better if gamma spatial distribution were expressed as dose, rather than number of photons. Not in time for the abstract submission, however!}
    \label{fig:GammaSpatialDistribution}
\end{figure}

@@

\begin{figure}
    \centering
    \vspace{2in}
    \subfloat[SUP]{
%	\todo{Add gamma dose versus energy at SUP, \SI{10.2}{\cm} collimator}\hspace{\columnwidth}
        \includegraphics[width=3in]{DoseVSenergySUP.eps}\hspace{\columnwidth}
        \label{fig:GammaDoseEnergySUP}
    }\\
    \subfloat[CUP]{
%     \todo{Add gamma dose versus energy at CUP, \SI{10.2}{\cm} collimator}\hspace{\columnwidth}
        \includegraphics[width=3in]{DoseVSenergyCUP.eps}\hspace{\columnwidth}
        \label{fig:GammaDoseEnergyCUP}
    }
    \caption{Gamma dose spectra}
    \label{fig:GammaDoseEnergy}
\end{figure}
